\vspace{-1cm} \bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}

### 2018-03-03 latex/paper.tex
Fix vertical spacing, change template to 'report' instead of 'article' type

\documentclass[12pt, twoside, letterpaper]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage[parfill]{parskip}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{charter}
\usepackage[numbers]{natbib}
\usepackage[draft]{graphicx}
\graphicspath{{../figures/}}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

\bibliographystyle{unsrtapalike}

@@

% new commands
\newcommand{\PIP}{PIP\textsubscript{2}}
\newcommand{\sigd}{$\beta$\textit{2t}-SigD}
\newcommand{\sktl}{\textit{sktl}}
\renewcommand*{\Affilfont}{\footnotesize \normalfont}
\renewcommand*{\Authfont}{\normalsize}

\title{\bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}}
\author[1,2]{Alind Gupta \thanks{\url{alind.gupta@mail.utoronto.ca}}}
\author[1,2]{Julie A. Brill \thanks{\url{julie.brill@sickkids.ca} (Corresponding author)}}
\affil[1]{\small Department of Molecular Genetics, University of Toronto, Toronto, ON M5S 1A8, Canada}
\affil[2]{\small Program in Cell Biology, Hospital for Sick Children, Toronto, ON M5G 1X8, Canada}
\date{}

@@

\maketitle
\raggedright

\begin{abstract}
  \vspace*{-0.7em}
  Cilia are sensory organelles that are important for human development
  and physiology.
  A large number of genetic disorders affecting cilia are associated with
  mutations in proteins that localize to the transition zone (TZ),
  a structure at the base of cilia required for ciliogenesis and
  regulation of trafficking in and out of the cilium.
  Here, we report that the membrane lipid phosphatidylinositol
  4,5-bisphosphate(\PIP{}) is essential for proper maturation and function
  of TZs in the male \textit{Drosophila melanogaster} germline.
  Reduction of cellular \PIP{} levels by expression of the
  \textit{Salmonella} phosphoinositide phosphatase SigD or mutation of
  the type I phosphatidylinositol phosphate kinase (PIPKI) Skittles (Sktl)
  induces hyperelongation of TZs following their docking at the plasma
  membrane.
  We provide evidence that these hyperelongated TZs are functionally
  defective, and that the Exo84 mutant \textit{onion rings}
  \textit{onr} decouples TZ hyperelongation from the role for
  \PIP{} in cilium-membrane tethering.
  Our observations reveals a requirement for \PIP{} at the base of cilia
  in regulating TZ length and function.
\end{abstract}

\section{Introduction}
Cilia are sensory organelles present on almost all cells in the human body
\citep{satir2010primary}.
They function primarily by providing sensory inputs to cells, but can
also function as motile propellers in certain cells
\citep{bloodgood2010sensory}.
Consistent with their importance in cell signalling,
defects in cilium formation are associated with genetic disorders
known collectively as ciliopathies, which can display
neurological defects \citep{valente2014primary},
skeletal abnormalities \citep{hammarsjo2017novel},
and infertility \citep{inaba2016sperm} in addition to other phenotypes
\citep{waters2011ciliopathies}.

A large number of ciliopathies are linked to mutations in proteins that
localize to the cilium transition zone (referred to herein as TZ).
The TZ is the proximal-most region of the cilium and
functions as a diffusion barrier that regulates the
bi-directional transport of protein and lipid cargo at the base of the cilium
\citep{reiter2012base, szymanska2012transition}.
The TZ is essential for cilium formation (ciliogenesis) and cilium-based
signalling.
The conserved TZ protein CEP290, for example, is mutated in at least
six different ciliopathies with a spectrum of clinical features and severities
, and is important for cilium formation
and function in both humans \citep{shimada2017vitro, stowe2012centriolar}
and Drosophila \citep{basiri2014migrating}.
Although the protein composition of TZs has been investigated in various
studies ranging from single gene analysis to proteomics,
processes underlying TZ maturation are not as well-studied.

@@

\section{Results}
\subsection{\PIP{} is essential for transition zone maturation}
To investigate whether reduction of cellular \PIP{} affects ciliogenesis in the
Drosophila male germline,
we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
under the $\beta$2-tubulin promoter (referred to herein as \sigd{}),
which is expressed exclusively in spermatocytes
\citep{wei2008depletion, fabian2010phosphatidylinositol}.
We previously showed that \sigd{} induces male sterility
due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
To examine whether this may be caused by aberrant TZ function,
we examined the localization of fluorescently-labelled
centriolar/basal body protein
Ana1 (CEP295 homolog) \citep{goshima2007genes, blachon2009proximal}
and the TZ protein Cep290 \citep{basiri2014migrating}
during early steps of cilium assembly in spermatocytes in
wild-type controls and \sigd{}.
As shown in Figure 1,
while Cep290 on nascent TZs look similar in wild-type and \sigd{}, 
it grew to significantly longer lengths in \sigd{}
compared to wild-type controls.
Ana1 lengths were not affected, and we did not observe an inverse
correlation between Cep290 and Ana1 length.
This hyperelongation phenotype was not specific to Cep290;
all TZ markers examined showed hyperelongation, including
acetylated tubulin \citep{gottardo2013cilium},
Chibby \citep{enjolras2012drosophila} and
MKS \citep{slaats2015mks1, vieillard2016transition} proteins (Figure 1D).
TZ hyperelongation was a highly penetrant phenotype (\textgreater 90\%)
and showed high intra-cyst correlation (\textgreater 0.95) suggestive
of a dosage-based response to a shared cellular factor,
presumably SigD.
Hyperelongated TZs persisted through meiosis.
Despite TZ hyperlongation, however, axonemes were able to
elongate post-meiosis (Figure 1E).
As we showed previously, the ultrastructure of these axonemes
was frequently aberrant,
either lacking symmetry completely or containing triplet microtubules
instead of doublets \citep{wei2008depletion}.

@@

\section{Discussion}
Cilia are tiny organelles that are essential for proper human development.
Many human disorders of cilia are associated with genes that encode
transition zone (TZ) proteins.
For example, mutations in the conserved TZ protein CEP290
are linked to more than 6 different ciliopathies,
ranging on a spectrum of clinical phenotypes and severities.
Most of these mutations are likely to be hypomorphic
and may be affected by genetic modifiers in affected individuals.
\citep{zaghloul2010functional, khanna2009common, leitch2008hypomorphic}.
Animal models with partial loss of TZ function may therefore
provide insight on intermediate phenotypes associated with human disease
and their cell biological basis.
In this paper, we described a novel role for the membrane lipid
phosphatidylinositol 4,5-bisphosphate (\PIP{}) in regulating TZ function.

@@

In humans, \textit{PIPKI$\gamma$} is linked to lethal congenital contractural
syndrome type 3 (LCCS3), which has been suggested to represent a ciliopathy
\citep{}.
The recent discovery of the role of LCCS1-associated GLE3 protein in cilia
further shows this.

@@

\section{Methods}
\subsection{Transgenic flies}
Drosophila stocks were cultured on cornmeal molasses agar medium at 25$^{\circ}$C
and 50\% humidity.
Stocks expressing $\beta$\textit{2t}::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3})
and $\beta$\textit{2t}::YFP-Sktl (chromosome \textit{2})
were described previously \citep{wei2008depletion, fabian2010phosphatidylinositol}.
$\beta$\textit{2t}::mCherry-Sktl was made as in \citep{wei2008depletion},
and a \textit{P}-element insertion on chromosome \textit{2} was used for rescue using the low-level
expression vector \textit{tv3} \citep{wong2005pip2}.
Ana1-tdTomato (chromosome \textit{2}) and Cep290-GFP (chromosome \textit{3}) were provided
by T. Avidor-Reiss \citep{basiri2014migrating}.
\textit{Sp}/\textit{CyO}; Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
Stocks expressing GFP-tagged Chibby, B9d1, B9d2, Cc2d2a and Mks1 were
provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
The \textit{onr} mutant was described previously \citep{giansanti2015exocyst}.
Stocks for generating \textit{sktl}\textsuperscript{2.3} clones were originally provided by
A. Guichet \citep{gervais2008pip5k}.
\textit{w}\textsuperscript{1118} was used as the wild-type control.

@@

@@

\section{Acknowledgements}
We thank Brian Ciruna for insightful comments on the project
and Bénédicte Durand for providing unpublished fly stocks.
This work was supported by a grant from the Canadian Institute for Health Research
(CIHR) to J.A.B.

@@

\newpage
\section{Figures}

%%
%    FIGURE 1
%
\textbf{Figure 1. SigD expression induces transition zone hyperelongation.}
\begin{enumerate}[label={\Alph*.}, nolistsep]
\item Schematic diagram of the stages of ciliogenesis in the Drosophila male germline.
  Stages in brackets correspond to those from \citep{cenci1994chromatin}.
\item \sigd{} expression induces Cep290 hyperelongation in late G2 cilia.
\item Paired Ana1-Cep290 lengths in early and late G2 phase in spermatocytes.
  Numbers in red represent correlation between Cep290 and Ana1 lengths.
\item \sigd{} expression induces hyperelongation of Chibby and Mks1.
\item TZ hyperelongation persists through meiosis but does not affect
  axoneme outgrowth.
\end{enumerate}

\begin{figure}[ht]
  \includegraphics[scale=0.9]{figure-1/figure1.png}
\end{figure}
\newpage

%%
%%%%
%%%    FIGURE 2
%%%
\textbf{Figure 2. Sktl is important for transition zone maturation and localizes to basal bodies.}
\begin{enumerate}[label={\Alph*.}, nolistsep]
\item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
\item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} ($n$\textgreater 60) from (A).
\item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
  Unc-GFP.
\item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
  The scale bar represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
\end{enumerate}

\begin{figure}[ht]
  \includegraphics[scale=0.9]{figure-2/figure2.png}
\end{figure}
\newpage

%%
%    FIGURE 3
%
\textbf{Figure 3. Hyperelongated transition zones display functional defects.}
\begin{enumerate}[label={(\Alph*)}, nolistsep]
\item
\item
\item
\item
\end{enumerate}

\begin{figure}[ht]
  \includegraphics[scale=0.8]{figure-3/figure3.png}
\end{figure}
\newpage

%%%
%%    FIGURE 4
%%
\textbf{Figure 4. The \textit{onion rings} (\textit{onr}) allele of \textit{d}Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}
\begin{enumerate}[label={(\Alph*)}, nolistsep]
\item Cells mutant for \textit{onr} do not display hyperelongated TZs marked with acetylated tubulin.
\item Quantification from (A).
\item Cells mutant for \textit{onr} display loss of plasma membrane tethering.
\end{enumerate}

\begin{figure}[ht]
  \includegraphics[scale=0.9]{figure-4/figure4.png}
\end{figure}
\newpage

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\documentclass[12pt, twoside, letterpaper]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage[parfill]{parskip}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{charter}
\usepackage[numbers]{natbib}
\usepackage{graphicx}
\graphicspath{{../figures/}}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{lineno}
\usepackage{setspace}

% bibliography style
\bibliographystyle{unsrtcurrbiol}

@@

% newcommand
\newcommand{\PIP}{PIP\textsubscript{2}}
\newcommand{\sigd}{$\beta$\textit{2t}-SigD}
\newcommand{\sktl}{\textit{sktl}}

% renewcommand
\renewcommand*{\Affilfont}{\footnotesize \normalfont}
\renewcommand*{\Authfont}{\normalsize}

\title{\vspace{-1cm} \bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}}
\author[1,2]{Alind Gupta \thanks{\url{alind.gupta@mail.utoronto.ca}}}
\author[1,2]{Julie A. Brill \thanks{\url{julie.brill@sickkids.ca} (Corresponding author)}}

\affil[1]{\small Department of Molecular Genetics, University of Toronto, Toronto, ON M5S 1A8, Canada}
\affil[2]{\small Program in Cell Biology, Hospital for Sick Children, Toronto, ON M5G 1X8, Canada}

\date{\small \today}

@@

\maketitle

\begin{doublespacing}
  \begin{linenumbers}

    \section{Summary}
    Cilia are sensory organelles that are essential for human development
    and physiology \citep{satir2010primary}.
    They function primarily by relaying extracellular stimuli to cells
    \citep{satir2010primary},
    but can also act as motile propellers in certain cell types
    \citep{bloodgood2010sensory}.
    A large number of genetic disorders linked to cilium dysfunction are
    associated with proteins that localize to the cilium transition zone (TZ),
    a structure at the base of cilia that regulates trafficking in and out
    of the cilium \citep{reiter2012base, szymanska2012transition}.
    Despite numerous efforts to elucidate TZ proteins and their functions,
    processes underlying maturation of TZs are not well understood.
    We report a role for the membrane lipid phosphatidylinositol 4,5-bisphosphate
    (\PIP{}) in TZ maturation and length regulation
    in the \textit{Drosophila melanogaster} male germline.
    Reduction of cellular \PIP{} levels by expression of the
    \textit{Salmonella} phosphoinositide phosphatase SigD or mutation of
    the type I phosphatidylinositol phosphate kinase (PIPKI) Skittles (Sktl)
    induced hyperelongation of TZs after they anchor at the plasma membrane.
    Hyperelongated TZs exhibit signs of functional defects, such as the inability
    to migrate and loss of membrane tethering.
    We also report that the Exo84 mutant \textit{onion rings} (\textit{onr})
    decouples TZ hyperelongation from loss of cilium-plasma membrane tethering.
    Our results reveal a requirement for \PIP{} in supporting ciliogenesis
    through TZ maintenance.

    \section{Results and Discussion}
    Cilia are sensory organelles present on almost all cells in the human body
    \citep{satir2010primary}.
    They are important for transducing signalling pathways in response to extracellular
    cues.
    Consistent with their importance in cell signalling,
    defects in cilium formation are associated with genetic disorders
    known collectively as ciliopathies, which can display
    neurological defects \citep{valente2014primary},
    skeletal abnormalities \citep{hammarsjo2017novel},
    and infertility \citep{inaba2016sperm} in addition to other phenotypes
    \citep{waters2011ciliopathies}.
    Many ciliopathies are associated with mutations in proteins that localize
    to the cilium transition zone (TZ), the proximal-most region of the cilium that
    functions as a diffusion barrier and regulates the
    bi-directional transport of protein and lipid cargo at the base of the cilium
    \citep{reiter2012base, szymanska2012transition}.
    The TZ is essential for cilium formation (ciliogenesis) and function.
    The conserved TZ protein CEP290, for example, is mutated in at least
    six different ciliopathies with a spectrum of clinical features and severities
    , and is important for cilium formation
    and function in both humans \citep{shimada2017vitro, stowe2012centriolar}
    and Drosophila \citep{basiri2014migrating}.
    Although the protein composition of TZs has been investigated in various
    studies ranging from single gene analysis to proteomics,
    processes underlying TZ maturation are relatively understudied.

@@

    \subsection{\PIP{} is essential for transition zone maturation}
    To investigate whether reduction of cellular \PIP{} affects ciliogenesis in the
    Drosophila male germline,
    we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
    under the $\beta$2-tubulin promoter (referred to herein as \sigd{}),
    which is expressed exclusively in spermatocytes
    \citep{wei2008depletion, fabian2010phosphatidylinositol}.
    We previously showed that \sigd{} induces male sterility
    due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
    To examine whether this may be caused by aberrant TZ function,
    we examined the localization of fluorescently-labelled
    centriolar/basal body protein
    Ana1 (CEP295 homolog) \citep{goshima2007genes, blachon2009proximal}
    and the TZ protein Cep290 \citep{basiri2014migrating}
    during early steps of cilium assembly in spermatocytes in
    wild-type controls and \sigd{}.
    As shown in Figure 1,
    while Cep290 on nascent TZs look similar in wild-type and \sigd{}, 
    it grew to significantly longer lengths in \sigd{}
    compared to wild-type controls.
    Ana1 lengths were not affected, and we did not observe an inverse
    correlation between Cep290 and Ana1 length.
    This hyperelongation phenotype was not specific to Cep290;
    all TZ markers examined showed hyperelongation, including
    acetylated tubulin \citep{gottardo2013cilium},
    Chibby \citep{enjolras2012drosophila} and
    MKS \citep{slaats2015mks1, vieillard2016transition} proteins (Figure 1D).
    TZ hyperelongation was a highly penetrant phenotype (\textgreater 90\%)
    and showed high intra-cyst correlation (\textgreater 0.95) suggestive
    of a dosage-based response to a shared cellular factor,
    presumably SigD.
    Hyperelongated TZs persisted through meiosis.
    Despite TZ hyperlongation, however, axonemes were able to
    elongate post-meiosis (Figure 1E).
    As we showed previously, the ultrastructure of these axonemes
    was frequently aberrant,
    either lacking symmetry completely or containing triplet microtubules
    instead of doublets \citep{wei2008depletion}.

@@

@@

    In humans, \textit{PIPKI$\gamma$} is linked to lethal congenital contractural
    syndrome type 3 (LCCS3), which has been suggested to represent a ciliopathy.
    The recent discovery of the role of LCCS1-associated GLE3 protein in cilia
    further shows this.

@@

    \section{Methods}
    \subsection{Transgenic flies}
    Drosophila stocks were cultured on cornmeal molasses agar medium at 25$^{\circ}$C
    and 50\% humidity.
    Stocks expressing $\beta$\textit{2t}::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3})
    and $\beta$\textit{2t}::YFP-Sktl (chromosome \textit{2})
    were described previously \citep{wei2008depletion, fabian2010phosphatidylinositol}.
    $\beta$\textit{2t}::mCherry-Sktl was made as in \citep{wei2008depletion},
    and a \textit{P}-element insertion on chromosome \textit{2} was used for rescue using the low-level
    expression vector \textit{tv3} \citep{wong2005pip2}.
    Ana1-tdTomato (chromosome \textit{2}) and Cep290-GFP (chromosome \textit{3}) were provided
    by T. Avidor-Reiss \citep{basiri2014migrating}.
    \textit{Sp}/\textit{CyO}; Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
    Stocks expressing GFP-tagged Chibby and Mks1 were
    provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
    The \textit{onr} mutant was described previously \citep{giansanti2015exocyst}.
    Stocks for generating \textit{sktl}\textsuperscript{2.3} clones were originally provided by
    A. Guichet \citep{gervais2008pip5k}.
    \textit{w}\textsuperscript{1118} was used as the wild-type control.

@@

    \section{Supplemental information}
    Includes two figures.

    \section{Acknowledgements}
    We are grateful to Brian Ciruna for insightful comments on the project,
    and Bénédicte Durand for providing (at the time of experiments)
    unpublished fly stocks.
    This work was supported by a grant from the Canadian Institute for
    Health and Research to J.A.B (Placeholder for Grant number).
    A.G. was supported by an Open Fellowship and Ontario Graduate Scholarship.

@@

    \section{Declaration of interests}
    The authors declare no competing interests.

    \section{Figures}

    \textbf{Figure 1. SigD expression induces transition zone hyperelongation.}
    \begin{enumerate}[label={(\Alph*)}, nolistsep]
    \item Schematic diagram of the stages of ciliogenesis in the Drosophila male germline.
      Stages in brackets correspond to those in \citep{cenci1994chromatin}.
    \item \sigd{} expression induces Cep290 hyperelongation in late G2 cilia.
    \item Paired Ana1-Cep290 lengths in early and late G2 phase in spermatocytes.
    \item \sigd{} expression induces hyperelongation of Chibby and Mks1 in late G2 phase.
    \item TZ hyperelongation persists through meiosis but does not affect
      axoneme outgrowth.
    \end{enumerate}

    \textbf{Figure 2. Sktl is important for transition zone maturation.}
    \begin{enumerate}[label={(\Alph*)}, nolistsep]
    \item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
    \item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} ($n$\textgreater 60) from (A).
    \item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
      Unc-GFP.
    \item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
      The scale bar represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
      Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
    \end{enumerate}

    \textbf{Figure 3. Hyperelongated transition zones display functional defects.}
    \begin{enumerate}[label={(\Alph*)}, nolistsep]
    \item 
    \item
    \item
    \item
    \end{enumerate}

    \textbf{Figure 4. The \textit{onion rings} (\textit{onr}) allele of \textit{d}Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}
    \begin{enumerate}[label={(\Alph*)}, nolistsep]
    \item Cells expressing \sigd{} do not maintain plasma membrane-cilium tethering. The plasma membrane is marked with CellMask.
    \item \textit{onr} mutants do not maintain plasma membrane-cilium tethering.
    \item Cells mutant for \textit{onr} do not display hyperelongated acetylated tubulin signal at the cilium.
    \item GFP-tagged Exo70 localizes to basal bodies.
    \end{enumerate}

  \end{linenumbers}
\end{doublespacing}

@@

%% 
% FIGURE 1
% 
% \textbf{Figure 1. SigD expression induces transition zone hyperelongation.}
% \begin{enumerate}[label={(\Alph*.)}, nolistsep]
% \item Schematic diagram of the stages of ciliogenesis in the Drosophila male germline.
%   Stages in brackets correspond to those from \citep{cenci1994chromatin}.
% \item \sigd{} expression induces Cep290 hyperelongation in late G2 cilia.
% \item Paired Ana1-Cep290 lengths in early and late G2 phase in spermatocytes.
%   Numbers in red represent correlation between Cep290 and Ana1 lengths.
% \item \sigd{} expression induces hyperelongation of Chibby and Mks1.
% \item TZ hyperelongation persists through meiosis but does not affect
%   axoneme outgrowth.
% \end{enumerate}
% 
% \begin{figure}[ht]
%   \includegraphics[scale=0.9]{figure-1/figure1.png}
% \end{figure}
% \newpage
% 
% %% 
% %%%% 
% %%% FIGURE 2
% %%% 
% \textbf{Figure 2. Sktl is important for transition zone maturation and localizes to basal bodies.}
% \begin{enumerate}[label={(\Alph*.)}, nolistsep]
% \item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
% \item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} ($n$\textgreater 60) from (A).
% \item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
%   Unc-GFP.
% \item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
%   The scale bar represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
%   Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
% \end{enumerate}
% 
% \begin{figure}[ht]
%   \includegraphics[scale=0.9]{figure-2/figure2.png}
% \end{figure}
% \newpage
% 
% 
% %% 
% % FIGURE 3
% % 
% \textbf{Figure 3. Hyperelongated transition zones display functional defects.}
% \begin{enumerate}[label={(\Alph*)}, nolistsep]
% \item
% \item
% \item
% \item
% \end{enumerate}
% 
% \begin{figure}[ht]
%   \includegraphics[scale=0.8]{figure-3/figure3.png}
% \end{figure}
% \newpage
% 
% 
% %%% 
% %% FIGURE 4
% %% 
% \textbf{Figure 4. The \textit{onion rings} (\textit{onr}) allele of \textit{d}Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}
% \begin{enumerate}[label={(\Alph*)}, nolistsep]
% \item Cells mutant for \textit{onr} do not display hyperelongated TZs marked with acetylated tubulin.
% \item Quantification from (A).
% \item Cells mutant for \textit{onr} display loss of plasma membrane tethering.
% \end{enumerate}
% 
% \begin{figure}[ht]
%   \includegraphics[scale=0.9]{figure-4/figure4.png}
% \end{figure}
% \newpage

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End
